Residual Ratios

### 2021-10-05 analysis/get_util_piece_size.Rmd
resdual ratios
stuff 6437

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
setwd("g:/Shared Drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
piece_size <- select(piece_size,-FMA)
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
species_prop <- read.csv(file = '../data/species_proportions_full.csv') %>%
  select(TRM,max_species)

@@

avepieceC
avepieceD

head(util_piece_fmu_twp_species)
#if (util_piece_fmu_twp_species$CD == "Decid") util_piece_fmu_twp_species$max_species <- "popu_tre"
tabyl(util_piece_fmu_twp_species,FMU,CD,show_na = TRUE)
#if (util_piece_fmu_twp_species$CD == "Decid") util_piece_fmu_twp_species$max_species <- "popu_tre"
#if (util_piece_fmu_twp_species$max_species == "pseu_men") util_piece_fmu_twp_species$max_species <- "pice_gla"

@@

tabyl(util_piece_fmu_twp_species,max_species,CD,show_na = TRUE)
head(util_piece_fmu_twp_species)
util_piece_fmu_twp_species
dbhCalcInput
```

>>>>

```{r libraries, echo=FALSE, message=FALSE}
setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
#setwd("g:/Shared Drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
piece_size <- select(piece_size,-FMA)
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
species_prop <- read.csv(file = '../data/species_proportions_full.csv') %>%
  select(TRM,max_species)
spp_lookup <- read.csv(file ='../data/species_lookup.csv')

@@

#avepieceC
#avepieceD

head(util_piece_fmu_twp_species)
#if (util_piece_fmu_twp_species$CD == "Decid") util_piece_fmu_twp_species$max_species <- "popu_tre"
#tabyl(util_piece_fmu_twp_species,FMU,CD,show_na = TRUE)
#if (util_piece_fmu_twp_species$CD == "Decid") util_piece_fmu_twp_species$max_species <- "popu_tre"
#if (util_piece_fmu_twp_species$max_species == "pseu_men") util_piece_fmu_twp_species$max_species <- "pice_gla"

@@

#tabyl(util_piece_fmu_twp_species,max_species,CD,show_na = TRUE)
#head(util_piece_fmu_twp_species)

rename(util_piece_fmu_twp_species,stump_d = stumpd)
rename(util_piece_fmu_twp_species,top_d = topd)
rename(util_piece_fmu_twp_species,stump_ht = stumpht)
rename(util_piece_fmu_twp_species,min_len = merch_len)
rename(util_piece_fmu_twp_species,merch_ib_vol = piece_size)

util_piece_fmu_twp_species <- left_join(util_piece_fmu_twp_species,spp_lookup)

rename(util_piece_fmu_twp_species,species = sp)

save(util_piece_fmu_twp_species,file="../data/util_piece_fmu_twp_species.RData")

util_piece_fmu_twp_species
spp_lookup
```

### 2021-10-05 analysis/residual_ratios.Rmd
stuff 6437

---
title: "Inverse Taper Models"
author:

@@

date: "2021-09-16"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
bibliography: historicalResidueSupply.bib
---

@@

## Taper

@@

residual_ratios <-
  read.csv(file = '../data/residual_ratios.csv', fileEncoding = 'UTF-8-BOM')
residual_ratios

>>>>

---
title: "Residual Ratios"
author:

@@

date: "`r format(Sys.time(), '%Y-%m-%d')`"
#date: "2021-09-16"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
bibliography: historicalResidueSupply.bib
---

@@

## Residual ratios

@@

residual_ratios <-
  read.csv(file = '../data/residual_ratios.csv', fileEncoding = 'UTF-8-BOM')
residual_ratios$prop_of_137 <- residual_ratios$merch_ib_vol / residual_ratios$merch_ib_vol137
residual_ratios
save(residual_ratios,file="../data/residualRatios.RData")
